---
title: "main-functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(measlesr)
```

## Functions for measlesr

### Function 1: `load_data()`

```{r}
load_data("cases_month")
```

This function loads in the measles data set from TidyTuesday. It takes in either `cases_month` or `cases_year` and loads in the appropriate data set. Alternatively, functions `load_month()` and `load_year()` also loads in the monthly and yearly measles datasets without needing a parameter.

---

### Function 2: `clean_measles()`

```{r}
clean_measles(load_month(), country = "Madagascar")
```

This function takes in either the monthly or yearly cases data set and returns a cleaned version. It drops NA values and renames columns. Optionally, the function can also filtered the cleaned data set by a given country.

---

### Function 3: `yearly_case_summary()`

```{r}
yearly_case_summary(country = "Madagascar")
```

This function takes in a country and returns a breakdown of that country's year-by-year measles cases. It displays each year's total number of cases, the percent change from the previous year, and declares the trend as stable, surging, or stable.

---

### Function 4: `filter_by_country()`

```{r}
filter_by_country(country = "Madagascar", by = "cases_month")
```

This function takes the user-specified dataset (monthly or yearly) and filters it by the given country.

---

### Function 5: `plot_monthly_cases()`

```{r}
plot_monthly_cases(year = 2018, country = "Madagascar")
```

This function creates a `ggplot` line graph plotting the provided country's number of measles cases per month during the specified year.

---


### Function 6: `plot_detection_methods()`

```{r}
plot_detection_methods(start_year = 2012, end_year = 2025)
```

This function creates a stacked bar graph showing the proportion of total measles cases found through each detection method: clinically-compatible, epidemiologically-linked, and lab confirmed. The function displays the proportion breakdown for the user-provided year range.

---

### Function 7: `linear_analysis()`

```{r}
linear_analysis()
```

This function creates a linear model of the relationship between total measles cases and air quality index (AQI). The model predicts log(average cases per country) using the AQI for the country. The function then returns the model analysis in the form of a table.

